Import OLIS spectral data

### 2023-12-04 Code/OlisImportPurCalc.Rmd
Tidied script. Removed redundant lines.
Fixed extraction of information from Filename column due to new data file path.

```{r set project variables, include = FALSE}
Project <- "PICO"
DataOut <- file.path("..", "GrowthAssessData")

#Sylwia's file path
#DataIn <- file.path("..", "OLISSpectraCorr", "SySlCCASingleTest", fsep = .Platform$file.sep)

#Mireille's file path
DataIn <- file.path("..", "OLISSpectraCorr", "MiSa", fsep = .Platform$file.sep)

DataInSpectra <- file.path("..", "ImportedData", "Jaz", fsep = .Platform$file.sep)

DataInPAR <- file.path("..", "MultiCultiSpectra", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "MireilleSavoieMSc", "Figures")

@@

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(plotly)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)

@@

TargetSpectraLong <- TargetSpectra %>%
  # rename(nm = OLIS.3D.ASCII) %>%
  separate(col = Filename, into = c("fp1", "fp2", "fp3", "SpectraDate", "Project", "Source", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE)

TargetSpectraLong2 <- TargetSpectraLong %>%
  select(-c(fp1, fp2, fp3, Type, Correction, Smooth)) %>% 
  rename(CultureID = Source) %>% 
  mutate(SpectraDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]"),
           SpectraDate = ymd(str_extract(SpectraDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

glimpse(TargetSpectraLong2)
```

Load Multiculti catalog
```{r load local multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
# MultiCulti metadata
MetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(MetaData)

MetaData <- MetaData %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`)) %>% 
  select(-c(...46,...47))

@@

OLISSpectraMeta <- MetaData %>%
  right_join(., TargetSpectraLong2, by = c("ID" = "CultureID"))

@@

remove(TargetSpectra)
remove(TargetSpectraLong)
remove(TargetSpectraLong2)
rm(MetaData)

glimpse(OLISSpectraMeta)
```
# remove extra columns from metacatelog
```{r remove columns}
 OLISSpectraMeta <- OLISSpectraMeta %>% 
  select(-c(OptodeMeasure,SampleID))

@@

#test for duplicate file names
unique(duplicated(OlisRdsFiles))
```
# Read .Rds, Summarize, Combine to single data frame

>>>>

```{r set project variables, include = FALSE}

Project <- "PICO"

DataIn <- file.path("..", "Data","RawData", "OLISSpectraCorr", fsep = .Platform$file.sep)

DataInCatalog <- file.path("..", "Data", fsep = .Platform$file.sep)

DataInSpectra <- file.path("..", "Data", "ProcessedData",  fsep = .Platform$file.sep)

DataInPAR <- file.path("..", "Data","RawData","MCEmissionSpectra", fsep = .Platform$file.sep)

DataOut <- file.path("..", "ProcessedData")

@@

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
# library(knitr)
# library(OneR)
library(zoo)
# library(strucchange)
# library(plotly)
# library(dplyr)
# library(magrittr)
# library(googledrive)
# library(googlesheets4)
library(readxl)

@@

TargetSpectra <- TargetSpectra %>%
  # rename(nm = OLIS.3D.ASCII) %>%
  separate(col = Filename, into = c("fp1", "fp2", "fp3", "fp4","SpectraDate", "Project", "CultureID", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE)

TargetSpectra <- TargetSpectra %>%
  select(-c(fp1, fp2, fp3, fp4, Type, Correction, Smooth)) %>% 
  mutate(SpectraDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]"),
           SpectraDate = ymd(str_extract(SpectraDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

glimpse(TargetSpectra)
```

Load Multiculti catalog
```{r load local multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}

# MultiCulti metadata filtered to include only runs for Prochlorococcus O2 Project
CultureCatalog <- readRDS(file = file.path(DataInCatalog, "CultureCatalog.Rds")) %>%

  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

CultureCatalog <- CultureCatalog %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`))

@@

OLISSpectraMeta <- CultureCatalog %>%
  right_join(., TargetSpectra, by = c("ID" = "CultureID"))

@@

remove(TargetSpectra)
remove(CultureCatalog)

glimpse(OLISSpectraMeta)

@@

#test for duplicate file names
unique(duplicated(OlisRdsFiles))
```

# Read .Rds, Summarize, Combine to single data frame
